Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium revision (\YellowPaperVersionNumber{})}}

### 2018-01-26 Paper.tex
\usepackage{seqsplit} & \seqsplit{0xcf416c536ec1a19ed1fb89e\\4ec7ffb3cf73aa413b3aa9b77d60e4fd81a4296ba}

@@

At block 2675119, in the transaction 
\texttt{0xcf416c536ec1a19ed1fb89e\\4ec7ffb3cf73aa413b3aa9b77d60e4fd81a4296ba}, an account at address 0x03 was called and an out-of-gas occurred during the call. Against the equation (\ref{eq:pre}), this added 0x03 in the set of touched addresses, and this transaction turned $\boldsymbol{\sigma}[0x03]$ into $\varnothing$.

>>>>

\usepackage{seqsplit}

@@

At block 2675119, in the transaction 
\seqsplit{0xcf416c536ec1a19ed1fb89e\\4ec7ffb3cf73aa413b3aa9b77d60e4fd81a4296ba}, an account at address 0x03 was called and an out-of-gas occurred during the call. Against the equation (\ref{eq:pre}), this added 0x03 in the set of touched addresses, and this transaction turned $\boldsymbol{\sigma}[0x03]$ into $\varnothing$.
